Output Summary

### 2023-09-11 03-post-process/ms-content/ms-content.Rmd
ms-content: update WUL-change figure
Based on reviewer comments:
* show three levels of WUL change: 50%, 100%, and 200%
* only show uncertainty for the "current scenario"
* use approx spawners instead of eggs
* include new row of plots showing resulting relationship between spawners and smolt at LGR

WUL_change_fig_caption = "
  Density-dependent survival relationships from egg (panels a-d) and parr (panels e-f) to smolt arriving at Lower Granite Dam (LGR) under current (solid lines) and increased (dashed lines) weighted usable habitat (WUL).
  Egg $\\to$ LGR survival includes density effects that are both direct (e.g., egg survival varies as a function of egg density) and indirect (parr size varies as a function of egg density, and survival varies with size), whereas parr $\\to$ LGR survival includes only the indirect density effects.
"
```

@@

```{r WUL-change-fig, fig.width = 7.2, fig.height = 4.5, eval = params$WUL_change_fig, fig.cap = WUL_change_fig_caption, time_it = TRUE}

@@

  # the parameters needed to calucate process model expected values
  the_params = c("alpha[pop]", "beta[pop]", "^lambda$",
                 "omega0[pop]", "omega1[pop]", "mu_pi[1,pop]",
                 "gamma0[1,pop]", "gamma1[1,pop]",
                 "gamma0[2,pop]", "gamma1[2,pop]",
                 "theta0[pop]", "theta1[pop]",
                 "tau0[pop]", "tau1[pop]"
  )

@@

get_phi_hat = function(x, E, WUL_change = 0, start = "E") {
  with(as.list(c(x, E = E, WUL_change = WUL_change)), {
    beta_hat = lambda * WUL

@@

    if (start == "E") out = Ma/E
    if (start == "Pb") out = Pb/E
    return(out)
  })
}

get_phi_hat_post = function(j, E_pred, WUL_change = 0, start = "E") {

@@

  out = sapply(1:nrow(the_samps), function(i) {
    x = prep_sample(the_samps, i = i, j = j)
    sapply(E_pred, function(e) get_phi_hat(x, E = e, WUL_change = WUL_change, start = start))
  })

@@

plot_f = function(j, start, WUL_change) {
  phi_real_post = get_phi_real_post(j = j, start = start)
  phi_real = post_summ(phi_real_post, ".")
  E_real = post_summ(post, sub_index("^E[.+,pop]", pop = j))
  E_pred = seq(min(E_real["mean",]), max(E_real["mean",]), length = 30)

  phi_hat_post = get_phi_hat_post(j = j, E_pred, start = start)
  phi_hat = post_summ(phi_hat_post, ".")
  phi_hat_new_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_change, start = start)
  phi_hat_new = post_summ(phi_hat_new_post, ".")

  plot(phi_real["mean",] ~ E_real["mean",], type = "n",
       ylim = make_lim(0, phi_hat[c("2.5%","97.5%"),],
                phi_hat_new[c("2.5%","97.5%"),]),
                # phi_real["mean",]),
       # ylim = make_lim(0, ifelse(start == "E", 0.075, 0.3)),
       xlim = c(0, max(E_real["mean",], E_pred)),
       xaxt = "n")

  # points(phi_real["mean",] ~ E_real["mean",], pch = 21, 
  #        col = "black", bg = scales::alpha("grey25", 0.25), cex = 0.8)

  polygon(x = c(E_pred, rev(E_pred)), 
          y = c(phi_hat["2.5%",], rev(phi_hat["97.5%",])),
          col = tranp_col, border = NA)
  lines(phi_hat["mean",] ~ E_pred, lwd = 2)
  lines(phi_hat["2.5%",] ~ E_pred)
  lines(phi_hat["97.5%",] ~ E_pred)

  polygon(x = c(E_pred, rev(E_pred)), 
          y = c(phi_hat_new["2.5%",], rev(phi_hat_new["97.5%",])),
          col = tranp_col, border = NA)
  lines(phi_hat_new["mean",] ~ E_pred, lwd = 2, lty = 2)
  lines(phi_hat_new["2.5%",] ~ E_pred,  lty = 2)
  lines(phi_hat_new["97.5%",] ~ E_pred, lty = 2)
  at_x = axisTicks(par("usr")[1:2], log = FALSE)
  axis(side = 1, at = at_x, labels = at_x/1e6)
  panel_label(paste0("(", letters[ifelse(start == "E", 0, 3) + j], ") ", pops[j]))

  if (j == 1) {
    if (start == "E") {
      axis_labels(ylab = "Egg \u2192 LGR Survival", outer = FALSE, yline = 1)
      legend("topright", title = "WUL", legend = c("Current", paste0("\u2191", WUL_change * 100, "%")), lty = c(1,2), seg.len = 1.5, bty = "n", cex = 0.8)
    } 
    if (start == "Pb") axis_labels(ylab = "Parr \u2192 LGR Survival", outer = FALSE, yline = 1)
  }

}

mypar(mfrow = c(2,4), col.axis = "black")
junk = sapply(1:4, function(j) plot_f(j, "E", 1))
junk = sapply(1:4, function(j) plot_f(j, "Pb", 1))
axis_labels(xlab = "Egg Production (Millions)")
```

>>>>

WUL_change_fig_caption = "
  Freshwater juvenile density-dependent relationships under current (solid lines) and increased (dashed lines) weighted usable habitat.
  Panels (_a_-_d_): composite survival from egg to smolt at Lower Granite Dam (LGR) including both direct (i.e., egg density affects egg survival via Beverton-Holt dynamics) and indirect (i.e., egg density affects growth rates, size affects parr and smolt survival) density effects; panels (_e_-_h_): composite survival from parr to smolt at LGR which includes only indirect effects; panels (_i_-_l_): smolt reaching LGR.
  Calculations operate based on density of juveniles -- _x_-axis converted to approximate spawner abundance (all ages, origins, and sexes) for ease of interpretation. Grey bands show the 95% credible region for the current relationship only; lines show posterior means.
"

obs_vs_fit_fig_caption = "
  Consistency between model fitted values (posterior means) and nearly all data sources with an explicit likelihood function; only parr and smolt mean length data have been omitted here for space.
  Each data point is one year for one population, with the exceptions of panels _g_, _h_, and _i_, which display values for both natural- and hatchery-origin survival rates, and in the cases of _h_ and _i_, these rates apply equally to all populations.
  More detailed visualizations of model fit are shown in Supplement B (Section 3: model fits as time series with magnitude of observation uncertainty shown; Section 11: diagnostics based on quantile-standardized residuals; Section 12: posterior predictive checks).
"
```

@@

```{r WUL-change-fig, fig.width = 7.2, fig.height = 6, eval = params$WUL_change_fig, fig.cap = msdown::prep_caption(WUL_change_fig_caption), time_it = TRUE}

@@

  # the parameters needed to calculate process model expected values
  the_params = c("alpha[pop]", "beta[pop]", "^lambda$",
                 "omega0[pop]", "omega1[pop]", "mu_pi[1,pop]",
                 "gamma0[1,pop]", "gamma1[1,pop]",
                 "gamma0[2,pop]", "gamma1[2,pop]",
                 "theta0[pop]", "theta1[pop]",
                 "tau0[pop]", "tau1[pop]"
  )

@@

get_phi_hat = function(x, E, WUL_change = 0, start = "E", out_type = "phi") {
  with(as.list(c(x, E = E, WUL_change = WUL_change)), {
    beta_hat = lambda * WUL

@@

    if (start == "E") out = Ma/E
    if (start == "Pb") out = Pb/E

    if (out_type == "phi") return(out)
    if (out_type == "Ma") return(Ma)
  })
}

get_phi_hat_post = function(j, E_pred, WUL_change = 0, start = "E", out_type = "phi") {

@@

  out = sapply(1:nrow(the_samps), function(i) {
    x = prep_sample(the_samps, i = i, j = j)
    sapply(E_pred, function(e) get_phi_hat(x, E = e, WUL_change = WUL_change, start = start, out_type = out_type))
  })

@@

plot_f = function(j, start, out_type) {

  WUL_changes = c(0.5, 1, 2)
  lwd = 1.5

  eps = mean(post_summ(post, sub_index("E_per_Sa[year,pop]", year = ".+", pop = j))["mean",])
  phi_real_post = get_phi_real_post(j = j, start = start)
  phi_real = post_summ(phi_real_post, ".")
  E_real = post_summ(post, sub_index("^E[.+,pop]", pop = j))
  # E_pred = seq(min(E_real["mean",]), max(E_real["mean",]), length = 30)
  E_pred = seq(eps * 100, max(E_real["mean",]), length = 30)
  keep_yrs = stringr::str_extract(colnames(E_real), "[:digit:]+,") |> 
    stringr::str_remove(",")

  S_pred = E_pred/eps
  S_real = post_summ(post, sub_index("^Sa_tot[year,pop]", year = keep_yrs, pop = j))

  phi_hat_post = get_phi_hat_post(j = j, E_pred, start = start, out_type = out_type)
  phi_hat = post_summ(phi_hat_post, ".")

  phi_hat_new1_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_changes[1], start = start, out_type = out_type)
  phi_hat_new1 = post_summ(phi_hat_new1_post, ".")
  phi_hat_new2_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_changes[2], start = start, out_type = out_type)
  phi_hat_new2 = post_summ(phi_hat_new2_post, ".")
  phi_hat_new3_post = get_phi_hat_post(j = j, E_pred, WUL_change = WUL_changes[3], start = start, out_type = out_type)
  phi_hat_new3 = post_summ(phi_hat_new3_post, ".")

  plot(phi_real["mean",] ~ S_real["mean",], type = "n",
       ylim = make_lim(0, phi_hat[c("2.5%","97.5%"),], phi_hat_new3["mean",]),
       # phi_real["mean",]),
       # ylim = make_lim(0, ifelse(start == "E", 0.075, 0.3)),
       xlim = c(0, max(S_real["mean",], S_pred)),
       xaxt = "n", yaxt = "n")

  # points(phi_real["mean",] ~ S_real["mean",], pch = 21,
  #        col = "black", bg = scales::alpha("grey25", 0.25), cex = 0.8)

  polygon(x = c(S_pred, rev(S_pred)), 
          y = c(phi_hat["2.5%",], rev(phi_hat["97.5%",])),
          col = tranp_col, border = NA)

  lines(phi_hat["mean",] ~ S_pred, lwd = lwd)
  lines(phi_hat_new1["mean",] ~ S_pred, lty = 3, lwd = lwd)
  lines(phi_hat_new2["mean",] ~ S_pred, lty = 2, lwd = lwd)
  lines(phi_hat_new3["mean",] ~ S_pred, lty = 5, lwd = lwd)

  at_x = axisTicks(par("usr")[1:2], log = FALSE)
  axis(side = 1, at = at_x, labels = at_x/1000)

  at_y = axisTicks(par("usr")[3:4], log = FALSE)
  axis(side = 2, at = at_y, labels = at_y/ifelse(out_type == "Ma", 1000, 1))

  base = ifelse(start == "E", 0, 4)
  base = ifelse(out_type == "Ma", 8, base)
  panel_label(paste0("(", letters[base + j], ") "))

  if (j == 1) {
    if (start == "E" & out_type == "phi") {
      axis_labels(ylab = "Egg \u2192 LGR Survival", outer = FALSE, yline = 2)
      legend("topright", title = "Weighted Habitat", legend = c("Current", paste0("\u2191", WUL_changes * 100, "%")), lty = c(1,3,2,5), seg.len = 2.7, bty = "n", lwd = lwd, cex = 0.9)
    } 
    if (start == "Pb" & out_type == "phi") axis_labels(ylab = "Parr \u2192 LGR Survival", outer = FALSE, yline = 2)
    if (out_type == "Ma") {
      axis_labels(ylab = "LGR Smolt", outer = FALSE, yline = 2)
      axis_labels(ylab = "Thousands", outer = FALSE, yline = 1, cex = 0.8, font = 3)
    } 
  }

  if (start == "E" & out_type == "phi") {
    mtext(side = 3, line = 0.15, font = 2, text = pops[j], cex = 1)
  }
}

mypar(mfrow = c(3,4), oma = c(2.5,2.5,1,0), col.axis = "black")
junk = sapply(1:4, function(j) plot_f(j, "E", "phi"))
junk = sapply(1:4, function(j) plot_f(j, "Pb", "phi"))
junk = sapply(1:4, function(j) plot_f(j, "Pb", "Ma"))
axis_labels(xlab = "Spawner Abundance")
axis_labels(xlab = "Thousands", outer = TRUE, xline = 1.5, cex = 0.8, font = 3)
```
